Map of 2018 snow algae sample locations

### 2019-11-29 code/2018_sample_map.Rmd
red dots; field info table (save kable not working)

```{r libs, include=F}
library(tidyverse)
library(lubridate)
library(ggmap)

@@

load(here::here("output/map/raw_google_map.rda")) # loads .rda called "algae_map"... not sure how avoid using.rda format, maybe png?
```

@@

full_map
```

@@

>>>>

<style>
table {
  background-color: white !important;
  color: black !important;
}
</style>
<!-- format the table black and white -->

```{r libs, include=F}
library(tidyverse)
library(lubridate)
library(ggmap)
library(ggrepel)
library(kableExtra)
library(magick)
library(formattable)

@@

load(here::here("output/map/raw_google_map.rda")) # loads .rda called "algae_map"... not sure how avoid using.rda format, maybe png?
```
```{r}
cities <- cities %>% 
  filter(name == "Vancouver")
```

```{r}
field_summary <-
  field %>%
  group_by(mountain) %>% 
  drop_na(lat, lon) %>% 
  arrange(date) %>% 
  summarise(n=n(), 
            mean_elev = mean(elev_m), 
            first_visit=min(date) %>% format("%b %d"), 
            last_visit= max(date) %>% format("%b %d"), 
            n_visits= length(unique(date)),
            lat=mean(lat),
            lon=mean(lon),
            date=min(date)) %>% 
  arrange(date) %>% 
  select(-date)

# paste(field$date %>% month(label=TRUE), field$date %>%day())
```

@@

full_map

full_map_2 <-
  ggmap(algae_map, extent = "device") +
  geom_point(data = field_summary, aes(x=lon, y=lat),
              size = 1, alpha=1, 
              color = "red") +
  geom_point(data = cities, shape = 15, color="white") +
  geom_text(data = cities, aes(label = name), hjust = 1.1, color="white") #+
  # geom_text_repel(data=field_summary,
  #                 aes(x=lon, y=lat, label=mountain),
  #                 size=3, vjust=-2, hjust=1) +
  # plot transparent boxes for layers
  # geom_label_repel(data=field_summary,
  #            aes(label=mountain),
  #            label.size = NA,
  #            alpha=0.5, 
  #             label.padding=.1, 
  #             na.rm=TRUE,
  #            seed=123) #+
  #   # plot a second layer exactly the same, the labels for boxes
  # geom_label_repel(data=field_summary,
  #        aes(x=lon, y=lat, label=mountain), 
  #        alpha=1, 
  #        size=3,
  #        segment.color="black",
  #        segment.size = 1, 
  #        seed=123)
 # xlim = c(1, 20)
full_map_2

#missing enchantments point, not on map
```

```{r}
# field_summary_kable <- 
  field_summary %>% 
  mutate(mean_elev = round(mean_elev,0),
         last_visit = if_else(last_visit==first_visit,"",last_visit),
         date_range= if_else(last_visit!="",paste(first_visit, last_visit, sep=" - "), first_visit)) %>% 
  select(mountain, date_range,  mean_elev, n_visits,n) %>% 
  dplyr::rename_all(str_to_title) %>%
  dplyr::rename("Date"=Date_range,"Elevation"=Mean_elev, "N. visits"=N_visits, "Total samples"=N) %>% 
  kable(booktabs=T, format = "html") %>%
  kable_styling("striped",full_width = F) %>%
  row_spec(0:14,color ="white",background ="black") %>% 
  column_spec(1:5, width = "5em")

# generated final via screenshot

  # couldnt get to work
  # tried 
  # https://haozhu233.github.io/kableExtra/save_kable_and_as_image.html
  # https://stackoverflow.com/questions/48834749/error-using-magick-r-to-import-pdf
  # got image_read_pdf to work, still not authorized error for image_read
  # https://stackoverflow.com/questions/42928765/convertnot-authorized-aaaa-error-constitute-c-readimage-453
  # as_image()
  # save_kable(file=paste0(getwd(),"/presentation/omics/field_tbl.pdf"))
  # kable_as_image(filename=paste0(getwd(),"/presentation/omics/field_tbl.pdf"))
field_summary_kable
```

@@

# save output for omics presentation
ggsave(filename = here::here("presentation/omics/map.png"))
